%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%% Simple LaTeX CV Template %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% NOTE: If you find that it says                                     %%
%%                                                                    %%
%%                           1 of ??                                  %%
%%                                                                    %%
%% at the bottom of your first page, this means that the AUX file     %%
%% was not available when you ran LaTeX on this source. Simply RERUN  %%
%% LaTeX to get the ``??'' replaced with the number of the last page  %%
%% of the document. The AUX file will be generated on the first run   %%
%% of LaTeX and used on the second run to fill in all of the          %%
%% references.                                                        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't like 10pt? Try 11pt or 12pt
\documentclass[10pt]{article}

% This is a helpful package that puts math inside length specifications
\usepackage{calc}
\usepackage[usenames,dvipsnames]{color}
\usepackage{multicol}


% Simpler bibsection for CV sections
% (thanks to natbib for inspiration)
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\vspace{-\baselineskip}\begin{list}{}{%
       \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}
\makeatother

% Layout: Puts the section titles on left side of page
\reversemarginpar

%
%         PAPER SIZE, PAGE NUMBER, AND DOCUMENT LAYOUT NOTES:
%
% The next \usepackage line changes the layout for CV style section
% headings as marginal notes. It also sets up the paper size as either
% letter or A4. By default, letter was used. If A4 paper is desired,
% comment out the letterpaper lines and uncomment the a4paper lines.
%
% As you can see, the margin widths and section title widths can be
% easily adjusted.
%
% ALSO: Notice that the includefoot option can be commented OUT in order
% to put the PAGE NUMBER *IN* the bottom margin. This will make the
% effective text area larger.
%
% IF YOU WISH TO REMOVE THE ``of LASTPAGE'' next to each page number,
% see the note about the +LP and -LP lines below. Comment out the +LP
% and uncomment the -LP.
%
% IF YOU WISH TO REMOVE PAGE NUMBERS, be sure that the includefoot line
% is uncommented and ALSO uncomment the \pagestyle{empty} a few lines
% below.
%

%% Use these lines for letter-sized paper
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=.9in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=0.5in,               % 1 inch margins
            includemp]{geometry}

%% Use these lines for A4-sized paper
%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

%% More layout: Get rid of indenting throughout entire document
\setlength{\parindent}{0in}

%% This gives us fun enumeration environments. compactitem will be nice.
\usepackage{paralist}

%% Reference the last page in the page number
%
% NOTE: comment the +LP line and uncomment the -LP line to have page
%       numbers without the ``of ##'' last page reference)
%
% NOTE: uncomment the \pagestyle{empty} line to get rid of all page
%       numbers (make sure includefoot is commented out above)
%
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
% \pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The title (name) with a horizontal rule under it
%
% Usage: \makeheading{name}
%
% Place at top of document. It should be the first thing.
\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\Large \bfseries #1}\\[-0.8\baselineskip]%
                 \rule{\columnwidth}{0.25pt}%
         \end{minipage}}

% The section headings
%
% Usage: \section{section name}
%
% Follow this section IMMEDIATELY with the first line of the section
% text. Do not put whitespace in between. That is, do this:
%
%       \section{My Information}
%       Here is my information.
%
% and NOT this:
%
%       \section{My Information}
%
%       Here is my information.
%
% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[3]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \small \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

% An environment IDENTICAL to outerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

% An environment IDENTICAL to innerlist that has better pre-list spacing
% when used as the first thing in a \section
\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{compactitem}[#1]}
        {\end{compactitem}\vspace{-.6\baselineskip}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]\vspace{-0.3\baselineskip}}

% For \url{SOME_URL}, links SOME_URL to the url SOME_URL
\providecommand*\url[1]{\href{#1}{#1}}
% Same as above, but pretty-prints SOME_URL in teletype fixed-width font
\renewcommand*\url[1]{\href{#1}{\texttt{#1}}}

% For \email{ADDRESS}, links ADDRESS to the url mailto:ADDRESS
\providecommand*\email[1]{\href{mailto:#1}{#1}}
% Same as above, but pretty-prints ADDRESS in teletype fixed-width font
%\renewcommand*\email[1]{\href{mailto:#1}{\texttt{#1}}}

%%%%%%%%%%%%%%%%%%%%%%%% End Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Evan Hubinger}

\section{Contact Information}
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table
%       (adjust it to your liking; default is 1.85in).
%
%\newlength{\rcollength}\setlength{\rcollength}{1.75in}
%
%\begin{tabular}[t]{@{}p{\textwidth-\rcollength-2.3in}p{2.3in}p{\rcollength}}
\begin{tabular}[t]{@{}p{4.2in}p{3.5in}}
\email{evanjhub@gmail.com} & \url{alignmentforum.org/users/evhub} \\
(925) 240-3826 & \url{github.com/evhub}
\end{tabular}

\section{Education}
  \textbf{Harvey Mudd College}, Claremont, CA
  \hfill Graduated: May 2019 \\
  \-\quad \textbf{B.S. in Mathematics and Computer Science}
  \hfill GPA: 3.912 \\
  \-\quad \textit{High Distinction, Honors in Mathematics, Dean's List}

  \blankline

  \textbf{The College Preparatory School}, Oakland, CA
  \hfill Graduated: May 2015

% \section{Programming Languages}
%   \begin{minipage}[t]{.21525\textwidth}
%   \textbf{Expert} \\
%   \verb|Python, Coconut|
%   \end{minipage}
%   \begin{minipage}[t]{.45475\textwidth}
%   \textbf{Proficient} \\
%   \verb|Go, JavaScript, C++, Haskell, Lean|
%   \end{minipage}
%   \begin{minipage}[t]{.33\textwidth}
%   \textbf{Knowledgeable} \\
%   \verb|R, Java, MATLAB, Mathematica|
%   \end{minipage}

\section{Summary}
AI safety research fellow at the Machine Intelligence Research Institute. Previously did theoretical AI safety research with Paul Christiano at OpenAI. Machine learning research experience working for HRL Laboratories and the Music Information Retrieval Lab at Harvey Mudd College. Professional software engineering experience at Google, Yelp, and Ripple. Author of the Coconut programming language.

\section{Papers}
\textbf{An overview of 11 proposals for building safe advanced AI}
\hfill May 2020 \\
\textit{Evan Hubinger}
\hfill \url{arxiv.org/abs/2012.07532} \\
A comparative analysis of 11 different, leading proposals for building safe advanced AI under the current machine learning paradigm. Analyzes each proposal on the four components of outer alignment, inner alignment, training competitiveness, and performance competitiveness.

\blankline

\textbf{Risks from Learned Optimization in Advanced Machine Learning Systems}
\hfill June 2019 \\
\textit{Evan Hubinger, Chris van Merwijk, Vladimir Mikulik, Joar Skalse, Scott Garrabrant} \\
\hfill \url{arxiv.org/abs/1906.01820} \\
Introduces the concept and the potential dangers of inner alignment and mesa-optimization, specifically discussing when a trained model might be an optimizer and how it might be misaligned.

\section{Research Experience}
\textbf{Research Fellow}
\hfill November 2019 -- Present \\
\textbf{Machine Intelligence Research Institute, Berkeley, CA} \\
$\bullet$ Wrote ``An overview of 11 proposals for building safe advanced AI,'' as detailed above. \\
$\bullet$ Produced two new alternative \href{https://openai.com/blog/debate/}{AI safety via debate} proposals, ``\href{https://www.alignmentforum.org/posts/YWwzccGbcHMJMpT45/ai-safety-via-market-making}{AI Safety via Market Making}'' and ``\href{https://www.alignmentforum.org/posts/dJSD5RK6Qoidb3QY5/synthesizing-amplification-and-debate}{Synthesizing Amplification and Debate}. \\
$\bullet$ Analyzed different alignment proposals from a computational complexity standpoint as in ``\href{https://arxiv.org/abs/1805.00899}{AI safety via debate},'' resulting in ``\href{https://www.alignmentforum.org/posts/N64THGX7XNCqRtvPG/alignment-proposals-and-complexity-classes}{Alignment Proposals and Complexity Classes}'' and ``\href{https://www.alignmentforum.org/posts/CtGH3yEoo4mY2taxe/weak-hch-accesses-exp}{Weak HCH Accesses EXP}.'' \\
$\bullet$ Produced \href{https://www.alignmentforum.org/users/evhub}{a wide variety of additional work on the Alignment Forum}, including ``Gradient hacking,'' ``Chris Olah's views on AGI safety,'' ``Understanding 'Deep Double Descent,''' ``Outer alignment and imitative amplification,'' ``Learning the prior and generalization,'' ``Clarifying inner alignment terminology,'' ``Homogeneity vs. heterogeneity in AI takeoff scenarios,'' and ``Operationalizing compatibility with strategy-stealing.'' \\
$\bullet$ Mentored Adam Shimi, Mark Xu, and Noa Nabeshima, resulting in work such as Adam Shimi’s ``\href{https://www.alignmentforum.org/posts/farherQcqFQXqRcvv/universality-unwrapped}{Universality Unwrapped}'' and Mark Xu’s ``\href{https://www.alignmentforum.org/posts/ocWqg2Pf2br4jMmKA/does-sgd-produce-deceptive-alignment}{Does SGD Produce Deceptive Alignment?}'' \\
$\bullet$ \href{https://futureoflife.org/2020/07/01/evan-hubinger-on-inner-alignment-outer-alignment-and-proposals-for-building-safe-advanced-ai/}{Was interviewed on the Future of Life Institute's AI Alignment Podcast}.

\blankline

\textbf{Member of Technical Staff, Intern}
\hfill June -- September 2019 \\
\textbf{OpenAI, San Francisco, CA} \\
$\bullet$ Interned on the safety team at OpenAI working under Paul Christiano to tackle theoretical safety questions on topics such as amplification and universality. \\
$\bullet$ Wrote ``\href{https://www.alignmentforum.org/posts/9Dy5YRaoCxH9zuJqa/relaxed-adversarial-training-for-inner-alignment}{Relaxed adversarial training for inner alignment},'' an in-depth analysis of how techniques such as adversarial training or transparency tools might be used to address the inner alignment problem. \\
$\bullet$ Wrote ``\href{https://www.alignmentforum.org/posts/fM5ZWGDbnjb7ThNKJ/are-minimal-circuits-deceptive}{Are minimal circuits deceptive?}'' an answer to Paul Christiano's long-time open question on the malignity of minimal circuits.

\blankline

\textbf{Team Member}
\hfill Fall 2018 -- Spring 2019 \\
\textbf{HRL Laboratories Clinic Team, Harvey Mudd College, Claremont, CA} \\
$\bullet$ Completed the entire design, implementation, and training of a deep reinforcement learning agent to tune quantum dots by controlling voltage gates embedded in a silicon heterostructure.

\blankline

\textbf{Lab Member}
\hfill Spring 2018 -- Spring 2019 \\
\textbf{Music Information Retrieval Lab, Harvey Mudd College, Claremont CA} \\
$\bullet$ Team lead on the Sheet ID team using machine learning image retrieval techniques to identify cell phone images of sheet music. \\
$\bullet$ Worked on using machine learning to identify beats in song recordings for the Live Song ID team.

\blankline

\textbf{Intern}
\hfill May -- August 2017 \\
\textbf{Machine Intelligence Research Institute, Berkeley, CA} \\
$\bullet$ Came up with the idea for, organized a research group for, and began work on the paper ``\href{arxiv.org/abs/1906.01820}{Risks from Learned Optimization in Advanced Machine Learning Systems},'' as detailed above. \\
$\bullet$ Worked on a confidential type theory project using the Lean theorem prover.

\section{Engineering Experience}
\textbf{Site Reliability Engineering Intern}
\hfill May -- August 2017 \\
\textbf{Google, Sunnyvale, CA} \\
$\bullet$ Worked as a Launch Coordination Engineer (LCE) developing the software Google uses to perform production readiness reviews of new product launches. \\
$\bullet$ Revamped the custom domain-specific language built by the LCE team to automate launch reviews.

\blankline

\textbf{Software Engineering Intern}
\hfill June -- August 2016 \\
\textbf{Yelp, San Francisco, CA} \\
$\bullet$ Primary author of Undebt, an open-source automated code refactoring tool with over 1,500 stars on GitHub. \\
$\bullet$ Wrote \href{engineeringblog.yelp.com/2016/08/undebt-how-we-refactored-3-million-lines-of-code.html}{a blog post on Undebt}, at the time Yelp's most popular blog post. \\
$\bullet$ Fixed errors in Yelp's configuration management that had previously taken down yelp.com. \\
$\bullet$ Rewrote Yelp's system for running large data processing operations in Elastic Map Reduce.

\blankline

\textbf{Software Engineering Intern}
\hfill June -- August 2014; June -- August 2015 \\
\textbf{Ripple, San Francisco, CA} \\
$\bullet$ Worked on designing Interledger, a trustless system for cross-currency transactions between arbitrary agents. \\
$\bullet$ Wrote a tool to do cryptographically secure generation of wallets for financial institutions.

\section{Personal Projects}
\textbf{The Coconut Programming Language}
\hfill October 2014 -- Present \\
\url{coconut-lang.org} \\
$\bullet$ Created the Coconut programming language, a functional programming language that supports pattern-matching, algebraic data types, TRE/TCO, and compiles to any Python version. \\
$\bullet$ Coconut has over 2,300 stars on GitHub; over \$1,500 in yearly support from individuals and companies including TripleByte and Kea on Open Collective; and has made the front page of r/Python, r/Programming, and twice on Hacker News. \\
$\bullet$ \href{us.pycon.org/2017/schedule/presentation/56}{Presented on Coconut at PyCon 2017}. \\
$\bullet$ Was interviewed on Coconut for \href{talkpython.fm/episodes/show/117/functional-python-with-coconut}{TalkPython}, \href{podcastinit.com/episode-112-coconut-with-evan-hubinger}{Podcast.\_\_init\_\_}, and \href{functionalgeekery.com/episode-94-evan-hubinger}{Functional Geekery}.

\blankline

\textbf{Minecraft Deep Learning}
\hfill November 2017 -- February 2018 \\
\url{github.com/evhub/minecraft-deep-learning} \\
Used Deep Q Learning to solve the task of navigating to a house in Minecraft during a snowstorm starting from a random location. Used imitation pre-training, Dueling Double DQN, and Boltzmann-Gumbel exploration.

\blankline

\textbf{BBopt}
\hfill September 2017 -- Present \\
\url{github.com/evhub/bbopt} \\
Developed a universal black box optimization framework for tuning hyperparameters.

% \blankline

% \textbf{cPyparsing}
% \hfill July 2017 \\
% \url{github.com/evhub/cpyparsing} \\
% Reimplemented PyParsing in Cython to achieve $\approx30\%$ better performance for Coconut and Undebt.

% \blankline

% \textbf{PyProver}
% \hfill March 2017 \\
% \url{github.com/evhub/pyprover} \\
% Developed a library for resolution theorem proving in first-order predicate logic.

% \blankline

% \textbf{The Rabbit Programming Language}
% \hfill April -- December 2014 \\
% \url{github.com/evhub/rabbit} \\
% Created the Rabbit programming language, a purely functional, interpreted, dynamically-typed scripting language built on top of Python. Wrote a technical paper describing the language.

\section{Open Source Contributions}
  \textbf{Keras-RL}
  Added support for Boltzmann-Gumbel exploration based on the paper ``Boltzmann Exploration Done Right'' and fixed an issue with the Normalized Advantage Functions implementation.

  \hfill November 2018, November 2017

  \textbf{Keras}
  Fixed an issue involving invalid serialization of Keras models.
  \hfill November 2017

  \textbf{Conda}
  Added support for advanced PEP 496 packaging features.
  \hfill May 2017

  \textbf{Typeshed}
  Added type annotations for the \verb|future_builtins| module.
  \hfill October 2016

  \textbf{Jupyter}
  Added support for custom syntax highlighting.
  \hfill July 2016

\section{Relevant Courses}
  \textbf{Machine Learning}
  \hfill Fall 2017

  \textbf{Neural Networks}
  \hfill Fall 2017

  \textbf{Bayesian Statistics}
  \hfill Spring 2018

  \textbf{Algorithms}
  \hfill Spring 2018

  \textbf{Mathematical Analysis II}
  \hfill Fall 2018

  \textbf{Representation Theory}
  \hfill Fall 2018

  \textbf{Abstract Algebra}
  \hfill Fall 2017

  \textbf{Image Processing and Object Recognition}
  \hfill Fall 2016

  \textbf{Advanced Differential Equations and Linear Algebra}
  \hfill Summer 2016

  \textbf{Multivariable Calculus}
  \hfill Summer 2016

  \textbf{Discrete Mathematics}
  \hfill Spring 2016

\section{Other Activities and Awards}
  \textbf{Harvey Mudd Physics Department Rojansky Writing Award Winner}
  \hfill May 2017 \\
  Awarded for the technical writing in my paper ``\href{evhub.github.io/papers/everett.pdf}{Multiple Worlds, One Universal Wave Function}.''

  \blankline

  Harvey Mudd Effective Altruism Club Leader (2017 -- 2019) --- AI Summer Fellows Program Attendee (2018, 2019) --- Effective Altruism Global Attendee (2017, 2019, 2020) --- World Wide Web Consortium Interledger Payments Community Group Member (2016) --- National Forensics League Honor Society Outstanding Distinction (2015) --- National Policy Debate Tournament of Champions Participant (2014, 2015)

%\section{Project Experience}
    %\textbf{Project Title}
    %\hfill \textbf{Dates -- You know the drill} \\
    %\textit{Where you were when you did the project} \\
    %Some sort of description goes here, preferably including
    %\href{google.com}{links} of some sort.

%\section{References}
%\begin{tabular}[t]{@{}p{3.0in}p{3.0in}}
%\textbf{Chris DeForeest}     & \textbf{Purujit Saha}  \\
%Tech Lead: Dremel SRE        & Tech Lead: Dremel Dev  \\                           \email{cdeforeest@google.com}        & \email{purujit@google.com}     \\
%\end{tabular}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------%
% The following is copyright and licensing information for
% redistribution of this LaTeX source code; it also includes a liability
% statement. If this source code is not being redistributed to others,
% it may be omitted. It has no effect on the function of the above code.
%----------------------------------------------------------------------%
% Copyright (c) 2007, 2008, 2009, 2010, 2011 by Theodore P. Pavlic
% Some modifications made by Aaron Gable, 2011.
% More modifications made my John Phillpot, 2015.
% More modifications made my Evan Hubinger, 2016.
%
% Unless otherwise expressly stated, this work is licensed under the
% Creative Commons Attribution-Noncommercial 3.0 United States License. To
% view a copy of this license, visit
% creativecommons.org/licenses/by-nc/3.0/us/ or send a letter to
% Creative Commons, 171 Second Street, Suite 300, San Francisco,
% California, 94105, USA.
%
% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS
% OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
% MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
% IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY
% CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT,
% TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE
% SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
%----------------------------------------------------------------------%
